---
title: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# rmarkdown::render("code/solution-code/amd-dplyr-ggplot-R.RMD", output_dir = "solutions")

# rmarkdown::render("current-file-name.RMD",
#                   output_dir = "solutions")

library(tidyverse)
amd_bugs = read.csv(here::here("data/AMD_bugs_joined.csv"))

```

```{r}
head(amd_bugs)
```


1. Summarize the data to get an average `mean_dm_g` for every site, and plot the data as a bar chart.   

```{r}
amd_bugs %>%
  group_by(site) %>%
  summarise(mean_dm = mean(mean_dm_g)) %>%
  ggplot(aes(x = site, 
             y = mean_dm)) +
  geom_bar(stat = "identity")
```

2. Summarize the data to get an average `mean_dm_g` for each category, and plot the data as a bar chart. 

```{r}
amd_bugs %>%
  group_by(category) %>%
  summarise(mean_dm = mean(mean_dm_g)) %>%
  ggplot(aes(x = category, 
             y = mean_dm)) +
  geom_bar(stat = "identity")
```

3. Summarize the data to get an average and a standard deviation (SD) `mean_dm_g` for each category, and plot the data as a bar chart with an errorbar. 

```{r}
amd_bugs %>%
  group_by(category) %>%
  summarise(mean_dm = mean(mean_dm_g),
            sd_dm = sd(mean_dm_g)) %>%
  ggplot(aes(x = category, 
             y = mean_dm,
             ymin = mean_dm - sd_dm,
             ymax = mean_dm + sd_dm)) +
  geom_bar(stat = "identity")+
  geom_errorbar()
```

4. Modify the data to make a bar chart of the number of `taxa` in each category.  

```{r}
amd_bugs %>%
  distinct(category, taxa) %>%
  group_by(category) %>%
  summarise(taxa_n = n()) %>%
  ggplot(aes(x = category, 
             y = taxa_n)) +
  geom_bar(stat = "identity")
```

5. Modify the data to make a scatter point graph of the number of `taxa` for each values in the `pca1` column.  
  * Make the size of the points = 3  
  * Map color to pca1 and use `scale_color_viridis_c()`  
  * run `?scale_color_viridis_c` to see what color `option`'s are available and choose one  

```{r}
amd_bugs %>%
  distinct(pca1, taxa) %>%
  group_by(pca1) %>%
  summarise(taxa_n = n()) %>%
  ggplot(aes(x = pca1, 
             y = taxa_n,
             color = pca1)) +
  geom_point(size = 3) +
  scale_color_viridis_c(option = "plasma",
                        end = 0.8) +
  theme_bw()
```

6. Modify the data to make a scatter point graph of the number of `taxa` for each values in the `pca1` column. This time, modify the code to include the `category` variable in your summary.    
  * Make the size of the points = 3  
  * Map color to `category` and use `scale_color_viridis_d()`  
  * `scale_color_viridis_d` has the same color options. Choose the same option you used above.  
  * set `direction = -1` to make the color pallette match above.   

```{r}
amd_bugs %>%
  distinct(pca1, category, taxa) %>%
  group_by(pca1, category) %>%
  summarise(taxa_n = n()) %>%
  ggplot(aes(x = pca1, 
             y = taxa_n,
             color = category)) +
  geom_point(size = 3) +
  scale_color_viridis_d(option = "plasma",
                        direction = -1,
                        end = 0.8) +
  theme_bw()
```