---
title: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# rmarkdown::render("code/solution-code/Tidyr-tree-biomass-R.RMD", output_dir = "solutions")

# rmarkdown::render("current-file-name.RMD",
#                   output_dir = "solutions")

library(tidyverse)
raw_data = read.csv(
  "http://jpomz.github.io/ENVS396-FA-2024/data/Macroplot_data_Rev.txt",
  sep = "\t")

```


1. Use the data pipeline (including `mutate()` and `pivot_longer()`) we developed in class to create a longer data frame with one row for each measured stem. Use dplyr's `filter` function to remove all of the girths that are zero and use `extract()` to get the stem number, making sure to `convert = TRUE` to make it a number class. Store this longer data frame as an object called `clean_data`, and display the result in your console.  
```{r}
clean_data <- raw_data %>%
  mutate(treeid = 1:nrow(raw_data)) %>%
  pivot_longer(TreeGirth1:TreeGirth5, names_to = "stem", values_to = "girth") %>%
  filter(girth != 0) %>%
  extract(stem, 'stem', 'TreeGirth(.)', convert = TRUE)
clean_data |>
  head()
```

2. Stems are measured in girth (*i.e., circumference*) rather than diameter.
   Use `mutate()` to convert girth to diameter using the following formula: `diameter = circumference / pi` and print the results in your console.    
```{r}
clean_data %>%
  mutate(
    diameter = girth / pi) |>
  head()
```

3. Add another line to your `mutate()` function which calculates tree mass from the new diameter column you made according to the following equation: `mass = 0.124 * diameter^2.53`. Save this new data frame as `tree_mass` and print the results to the console. 
```{r}
tree_mass <- clean_data %>%
  mutate(
    diameter = girth / pi,
    mass = 0.124 * diameter^2.53) 
tree_mass |>
  head()
```

4. Estimate the total biomass by summing the mass of all of the stems in the `tree_mass` data.
```{r}
sum(tree_mass$mass)
```

5. The `SpCode` column contains information on the genus and specific epithet (species). Use `separate()` on the `SpCode` column to make a `GenusCode` and `SpEpCode` columns by separating them at position 4. Then use `group_by` and `summarize` to calculate the total biomass for each unique `GenusCode`.
```{r}
tree_mass %>%
  separate(SpCode, c("GenusCode", "SpEpCode"), 4) %>%
  group_by(GenusCode) %>%
  summarize(biomass = sum(mass))
```

6. Use ggplot to make a histogram of the `diameter` values in your `tree_mass` object. Make the x label `"Diameter [cm]` and the y label `"Number of Stems"`

```{r}
ggplot(tree_mass,
       aes(x = diameter)) +
  geom_histogram() +
  xlab("Diameter [cm]") +
  ylab("Number of stems")
```

