---
title: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# rmarkdown::render("code/solution-code/Tidyr-surveys-R.RMD", output_dir = "solutions")

# rmarkdown::render("current-file-name.RMD",
#                   output_dir = "solutions")

library(tidyverse)
surveys = read.csv(here::here("data/surveys.csv"))

```


1. Use `filter()` to remove all `NA` values from the `weight` column. Use `head()` to print the first few rows of your new object.  

```{r}
surveys |>
  filter(!is.na(weight)) |>
  head()
```

2. Use `unite()` to make a new column called `date_plot` which combines the `year`, `month`, `day`, and `plot_id` columns. Use `head()` to print out the first few rows of this object.  

```{r}
surveys |>
  filter(!is.na(weight)) |> # year == 1994, plot_id == 1
  unite('date_plot', year, month, day, plot_id) |>
  head()
```

3. Group your data by `date_plot` and `species_id` and summarize the mean `weight` for each group. Use `head()` to print out the first few rows of this object.  

```{r}
surveys |>
  filter(!is.na(weight)) |> # year == 1994, plot_id == 1
  unite('date_plot', year, month, day, plot_id) |>
  group_by(date_plot, species_id) |>
  summarize(mean_weight = mean(weight)) |>
  head()
```

4. Use `pivot_wider` to make a new data object with `species_id` in the columns and `weight` in the cells. Use `head()` to print out the first few rows of this object.  

```{r}
surveys |>
  filter(!is.na(weight)) |> # year == 1994, plot_id == 1
  unite('date_plot', year, month, day, plot_id) |>
  group_by(date_plot, species_id) |>
  summarize(mean_weight = mean(weight)) |>
  pivot_wider(names_from = species_id, values_from = mean_weight) |>
  head()
```


5. Begin a new data pipeline using the original `surveys` data object. Use `filter()` to remove all `NA` values from weight, keep only the `DM` species, and remove all empty values (i.e., `""`) of `sex`. Use `head()` to print out the first few rows of this object.  
```{r}
surveys |>
  filter(!is.na(weight),
         species_id == "DM",
         sex != "") |> 
  head()
```

6. `unite()` the `species_id` and `sex` column into a new `sp_sex` column. Use `head()` to print out the first few rows of this object.  
```{r}
surveys |>
  filter(!is.na(weight),
         species_id == "DM",
         sex != "") |> 
  unite("sp_sex", species_id, sex) |>
  head()
```

7. Group the data by `year` and `sp_sex` to calculate the mean weight. Use `head()` to print out the first few rows of this object.  
```{r}
surveys |>
  filter(!is.na(weight),
         species_id == "DM",
         sex != "") |> 
  unite("sp_sex", species_id, sex) |>
  group_by(year, sp_sex) %>%
  summarise(mean_weight = mean(weight)) |>
  head()
```

8. Starting with your summarized data, `separate()` `sp_sex` into a `species` and `sex` column and then use `ggplot()` to make a scatter graph of mean weight by year, and color the points according to `sex`. Also add linear regression lines to your plot, one for males and one for females. 
```{r, message=FALSE, warning=FALSE}
surveys |>
  filter(!is.na(weight),
         species_id == "DM",
         sex != "") |> 
  unite("sp_sex", species_id, sex) |>
  group_by(year, sp_sex) %>%
  summarise(mean_weight = mean(weight)) |>
  separate(sp_sex, c("sp", "sex"), sep = "_") |>
  ggplot(aes(x = year, y = mean_weight, color = sex)) +
  geom_point() +
  stat_smooth(method = "lm")
```

